\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeCompanyHeading}[2]{
  \par\addvspace{0.95\baselineskip}
  \noindent\begin{tabular*}{\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} & \small #2 \\
    \end{tabular*}\par
  \vspace{0.28\baselineskip}
}

\newcommand{\resumeRoleHeading}[2]{
  \par\addvspace{0.45\baselineskip}
  \noindent\begin{tabular*}{\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\par
  \vspace{0.10\baselineskip}
}

\newcommand{\resumeBullet}[1]{
  \par\noindent\small\makebox[0pt][r]{\raisebox{0.25ex}{\tiny$\bullet$}\hspace{0.6em}}#1\par
  \vspace{1pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Samuel Taylor} \\ \vspace{1pt}
    \small +65 8438 8860 $|$ \href{mailto:sam.j.a.taylor@gmail.com}{\underline{sam.j.a.taylor@gmail.com}} $|$
    \href{https://www.linkedin.com/in/samjataylor}{\underline{linkedin.com/in/samjataylor}}
\end{center}

%-----------SUMMARY-----------
\section{Profile}
\small{
Strategy and operations leader with experience across payments, GTM, pricing, and startup execution. Built cross-functional programs, commercial insights, and operational systems that unlocked growth, improved efficiency, and supported complex market launches across APAC and global teams.
}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeCompanyHeading
  {Stripe Payments}{Singapore}
\resumeRoleHeading
  {Global Strategy and Operations}{2022 -- Current}
\resumeBullet{Designed the operationalisation strategy for GCN across Risk, Product, Operations, and GTM teams.}
\resumeBullet{Ran international sticker-pricing analysis with the Pricing team, supporting approximately \$27M in annual value.}
\resumeBullet{Built a RISA-compliant onboarding strategy for Japan, helping secure the relationship with SMCC.}
\resumeBullet{Reformulated sold-guidance ratios for APAC, delivering approximately \$500K per year in incremental ONR.}
\resumeBullet{Initiated sales plays for account-to-account and BNPL offerings, generating more than \$200K in ONR for APAC GTM.}
\resumeBullet{Saved approximately \$1M per year in network costs through fee-code audits and launched currency-specific FX pricing for APAC GTM.}

\resumeCompanyHeading
  {Scortex}{France / Singapore}
\resumeRoleHeading
  {Deployment Director}{2021 -- 2022}
\resumeBullet{Served on the executive team with responsibility for all customer deployments, leading a delivery team of 3 to 4 people.}
\resumeBullet{Managed a 3x increase in project load within the first six months while maintaining delivery quality.}
\resumeBullet{Updated internal processes across hiring rubrics, technical specifications, and third-party contracts.}

\resumeCompanyHeading
  {Arcstone}{Singapore}
\resumeRoleHeading
  {MBA Intern}{2020}
\resumeBullet{Developed pricing strategy with the executive team for two SaaS MES products across Southeast Asia and Taiwan.}

\resumeCompanyHeading
  {Morgan Advanced Materials}{UK / Singapore / China / India}
\resumeRoleHeading
  {Senior Business Operations Analyst}{2019}
\resumeBullet{Reported directly to the divisional CFO to support the digital transformation of sales analytics capability.}
\resumeRoleHeading
  {Business Operations Analyst}{2016 -- 2019}
\resumeBullet{Promoted from a site role into global projects, reporting directly to the divisional COO.}
\resumeBullet{Managed a 12-week strategy review covering approximately \$500M in revenue with an external management consultancy.}
\resumeRoleHeading
  {Quality Engineer}{2015 -- 2016}
\resumeBullet{Reduced complaints by 36\% across the business's largest UK aerospace site.}
\resumeRoleHeading
  {Graduate Engineer}{2013 -- 2015}
\resumeBullet{Trialled a new packaging methodology across five Asian manufacturing sites for the Asian Operations Director.}

%-----------EDUCATION-----------
\section{Education}
\resumeCompanyHeading
  {INSEAD}{Singapore}
\resumeRoleHeading
  {MBA}{2020}
\resumeBullet{GMAT: 720}
\resumeBullet{Sainsbury Management Fellows Scholarship and Louis Franck Scholarship}

\resumeCompanyHeading
  {University of Manchester}{UK / USA}
\resumeRoleHeading
  {Masters in Chemistry}{2009 -- 2013}
\resumeBullet{First Class Degree; received the Manchester Success Scholarship}
\resumeBullet{Year abroad at the University of California, Santa Barbara}

%-----------ADDITIONAL-----------
\section{Additional Information}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English (Native)} \\
     \textbf{Other}{: Developing the online web tool XmRit! for process control analysis}
    }}
 \end{itemize}

\end{document}
